---
title: "Project Dengue virus 1"
author: '@Haruo_Suzuki'
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Abstract
[デング熱](https://ja.wikipedia.org/wiki/デング熱)とは、デングウイルス（Dengue virus）が原因の感染症である。
DEN-1デング熱ウイルスのゲノム配列データを取得し、DNA配列の統計値（長さ、GC含量）を計算した。それらの値は、メタデータ <ftp://ftp.ncbi.nlm.nih.gov/genomes/GENOME_REPORTS> における値 (`Size`, `GC%` ) と一致した。

# R For Bioinformatics

https://github.com/haruosuz/r4bioinfo/blob/master/R_Avril_Coghlan/README.md

```{r}
#install.packages("seqinr")
library("seqinr") # write.fasta # read.fasta # GC # rho
```

## Metadata
**[メタデータ](https://ja.wikipedia.org/wiki/メタデータ)**

https://github.com/haruosuz/DS4GD/blob/master/2019/CaseStudy.md#ncbi-genome_reports

```{r}
url <- "ftp://ftp.ncbi.nlm.nih.gov/genomes/GENOME_REPORTS/viruses.txt" # 5.3 MB
#url <- "ftp://ftp.ncbi.nlm.nih.gov/genomes/GENOME_REPORTS/plasmids.txt" # 2.6 MB
#url <- "ftp://ftp.ncbi.nlm.nih.gov/genomes/GENOME_REPORTS/eukaryotes.txt" # 2.7 MB
#url <- "ftp://ftp.ncbi.nlm.nih.gov/genomes/GENOME_REPORTS/prokaryotes.txt" # 71.8 MB
filename <- basename(url)
#download.file(url = url, destfile = filename)
#getwd() #system("open .")
d <- read.delim(file = filename, stringsAsFactors=FALSE, na.strings="-", check.names=FALSE)
dim(d)
#str(d)
#head(d, 2)
colnames(d)

# grepl returns a logical vector (match or not for each element of x)
organism_name <- "Dengue virus 1"
TF <- grepl(pattern = organism_name, x = d$`#Organism/Name`, ignore.case=TRUE)
d[TF,]
```

## Sequence data
**ゲノム配列データの取得**

https://github.com/haruosuz/r4bioinfo/blob/master/R_Avril_Coghlan/README.md#retrieving-genome-sequence-data-using-seqinr

```{r}
# Retrieving a DNA sequence from NCBI
library("seqinr")
ACCESSION <- "NC_001477" # Dengue virus 1
filename <- paste0("http://togows.org/entry/nucleotide/",ACCESSION,".fasta")
seqs <- read.fasta(file=filename, seqtype="DNA", strip.desc=TRUE)
# write the sequences to a FASTA-format file
write.fasta(sequences=seqs, names=getAnnot(seqs), file.out="mySequences.fna")
```

## Statistics
**DNA配列の統計（長さ、塩基組成、GC含量）**

https://github.com/haruosuz/r4bioinfo/blob/master/R_Avril_Coghlan/README.md#length-of-a-dna-sequence

```{r}
seq1 <- seqs[[1]] # Get the 1st sequence
seq1[1:10] # The first 10 nucleotides of the sequence
summary(seq1)
```

- The length of the DNA sequence is `r length(seq1)` nucleotides.
- Base composition (the number of As, Cs, Gs, and Ts) in the DEN-1 Dengue virus sequence is as follows: `r table(seq1)`.
- The GC content of the DNA sequence is `r GC(seq1)`.

# References
- https://github.com/haruosuz/bioinfo/blob/master/2020/README.wasedajuku.md
- R for Data Science [27 R Markdown](https://r4ds.had.co.nz/r-markdown.html)
27.4.6 Inline code
- [Dengue virus 1, complete genome - Nucleotide - NCBI](https://www.ncbi.nlm.nih.gov/nuccore/NC_001477)
